Supplementary Material

### 2020-02-06 Revisions/Beauchesne-eDriversMS-SI.rmd
setup files for revisions

---
title: Supplementary Material
fontsize: 12pt
output:
  pdf_document:
    toc: false
    number_sections: true
  html_document:
    number_sections: true
header-includes:
    - \usepackage{float}
    - \usepackage{setspace}
    - \onehalfspacing
relativeurls: true
bibliography: eDriversMS.bib
csl: frontiers.csl
link-citations: yes
---

>>>>

---
title: Supplementary Material
fontsize: 12pt
output:
  pdf_document:
    toc: false
    number_sections: true
    keep_tex: true
  html_document:
    number_sections: true
header-includes:
    - \usepackage{float}
    - \usepackage{setspace}
    - \onehalfspacing
relativeurls: true
bibliography: eDriversMS.bib
csl: frontiers.csl
link-citations: yes
---
